---
title: "viralpep_analysis_ISRE"
output:
  pdf_document: default
  html_document: default
date: "2022-09-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load in tidyverse
super useful library with simplified r functionality

```{r}
library(tidyverse)
```

## Read in data 

```{r}
setwd("C:/Users/lizke/Documents/research/FB/oncovirus")
hilo <- read.csv("ISREHI_ISRELO.csv", header=TRUE)
hipre <- read.csv("ISREHI_ISREpre.csv", header=TRUE)
lopre <- read.csv("ISRELO_ISREpre.csv", header=TRUE)

#use ggplot to create bar charts comparing counts of each subtype of peptides in the library sample
hilo_type <- ggplot(hilo, aes(y = Type2)) + 
  geom_bar(fill = "blue") + 
  labs(x = "Count", y = "Type", title = "HILO") + 
  theme_bw()

hipre_type <- ggplot(hipre, aes(y = Type2)) + 
  geom_bar(fill = "red") + 
  labs(x = "Count", y = "Type", title = "HIpre") + 
  theme_bw()

lopre_type <- ggplot(lopre, aes(y = Type2)) + 
  geom_bar(fill = "green") + 
  labs(x = "Count", y = "Type", title = "LOpre") + 
  theme_bw()

hilo_type
hipre_type
lopre_type
```

## Filter data to collect only significant hits: 
Peptides change in same direction, peptides have significant q-values in both reps, peptides have significant fold changes in both reps.

```{r filter_vplib_data}
hilo_sig <- filter(hilo, Direction=="Same" & Q_value_1<0.001&Q_value_2<0.001&Q_value_3<0.001 & abs(LFC1)>1&abs(LFC2)>1&abs(LFC3)>1)

hipre_sig <- filter(hipre, Direction=="Same" & Q_value_1<0.001&Q_value_2<0.001&Q_value_3<0.001 & abs(LFC1)>1&abs(LFC2)>1&abs(LFC3)>1)

lopre_sig <- filter(lopre, Direction=="Same" & Q_value_1<0.001&Q_value_2<0.001&Q_value_3<0.001 & abs(LFC1)>1&abs(LFC2)>1&abs(LFC3)>1)

hilo_type <- ggplot(hilo_sig, aes(y = Type2)) + 
  geom_bar(fill = "blue") + 
  labs(x = "Count", y = "Type", title = "HILO") + 
  theme_bw()

hipre_type <- ggplot(hipre_sig, aes(y = Type2)) + 
  geom_bar(fill = "red") + 
  labs(x = "Count", y = "Type", title = "HIpre") + 
  theme_bw()

lopre_type <- ggplot(lopre_sig, aes(y = Type2)) + 
  geom_bar(fill = "green") + 
  labs(x = "Count", y = "Type", title = "LOpre") + 
  theme_bw()

hilo_type
hipre_type
lopre_type
```

## Tiling
OK so now lets get the subtype of data we are most interested in, tiling peptides

```{r get_tiles}
hilo_tiling <- filter(hilo_sig, Type2 == "Tiling")
hilo_tiling$viral_protein <- paste(hilo_tiling$gene_name,hilo_tiling$Virus)

hipre_tiling <- filter(hipre_sig, Type2 == "Tiling")
hipre_tiling$viral_protein <- paste(hipre_tiling$gene_name,hipre_tiling$Virus)

lopre_tiling <- filter(lopre_sig, Type2 == "Tiling")
lopre_tiling$viral_protein <- paste(lopre_tiling$gene_name,lopre_tiling$Virus)

hilo_tiling
hipre_tiling
lopre_tiling
```

## Making some graphs with the data
here are a couple ggplot code chunks to visualize tiling peptide hits

```{r tiles_per_virus, fig.height=6, fig.width=4}
hilo_tiles_per_virus <- ggplot(hilo_tiling, aes(y = fct_infreq(Virus))) +
  geom_bar(fill = "blue") + 
  labs(x = "Tiles", y = "Virus", title = "Tiles per Virus - HILO") + 
  theme_bw()

hipre_tiles_per_virus <- ggplot(hipre_tiling, aes(y = fct_infreq(Virus))) +
  geom_bar(fill = "red") + 
  labs(x = "Tiles", y = "Virus", title = "Tiles per Virus - HIpre") + 
  theme_bw()

lopre_tiles_per_virus <- ggplot(lopre_tiling, aes(y = fct_infreq(Virus))) +
  geom_bar(fill = "green") + 
  labs(x = "Tiles", y = "Virus", title = "Tiles per Virus - LOpre") + 
  theme_bw()

hilo_tiles_per_virus
hipre_tiles_per_virus
lopre_tiles_per_virus
```

```{r tiles_per_gene, fig.height=30, fig.width=10}
hilo_tiles_per_protein <- ggplot(hilo_tiling, aes(y = fct_infreq(viral_protein))) + 
  geom_bar(fill="skyblue") + 
  labs(x = "Tiles", y = "Gene", title = "Tiles per Gene - HILO") + 
  theme_bw() +
  scale_x_continuous(breaks=seq(0,15,by=1))

hipre_tiles_per_protein <- ggplot(hipre_tiling, aes(y = fct_infreq(viral_protein))) + 
  geom_bar(fill="brown1") + 
  labs(x = "Tiles", y = "Gene", title = "Tiles per Gene - HIpre") + 
  theme_bw() +
  scale_x_continuous(breaks=seq(0,15,by=1))

lopre_tiles_per_protein <- ggplot(lopre_tiling, aes(y = fct_infreq(viral_protein))) + 
  geom_bar(fill="darkseagreen") + 
  labs(x = "Tiles", y = "Gene", title = "Tiles per Gene - LOpre") + 
  theme_bw() +
  scale_x_continuous(breaks=seq(0,15,by=1))

hilo_tiles_per_protein
hipre_tiles_per_protein
lopre_tiles_per_protein

```

## Enriched/depleted peptides and finding overlaps

```{r enriched_depleted_tiles HILO}
#enriched = need at least 100 reads in at least one 'Treat' condition #depleted = need at least 100 reads in at least one 'Control' condition
hilo_enr <- filter(hilo_tiling,LFC1>0&LFC2>0&LFC3>0&((ISREHI.rep1>100&ISREHI.rep2>100)|(ISREHI.rep1>100&ISREHI.rep3>100)|(ISREHI.rep2>100&ISREHI.rep3>100)))
hilo_dep <- filter(hilo_tiling,LFC1<0&LFC2<0&LFC3<0&((ISREHI.rep1>100&ISREHI.rep2>100)|(ISREHI.rep1>100&ISREHI.rep3>100)|(ISREHI.rep2>100&ISREHI.rep3>100)))

overlap <- filter(hilo_enr,hilo_enr$viral_protein %in% hilo_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

overlap2 <- filter(hilo_dep,hilo_dep$viral_protein %in% hilo_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

overlap <- rbind(overlap,overlap2)

enr_only <- filter(hilo_enr,!(hilo_enr$viral_protein %in% hilo_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

dep_only <- filter(hilo_dep,!(hilo_dep$viral_protein %in% hilo_enr$viral_protein)) %>%
select(viral_protein,LFC1,LFC2,LFC3, ID,protein)

hilo_overlap_venn <- distinct(overlap,viral_protein)
hilo_enr_only_venn <- distinct(enr_only,viral_protein)
hilo_dep_only_venn <- distinct(dep_only,viral_protein)

overlap
enr_only
dep_only

write.csv(overlap,"HILO_overlapping_prot.csv")
write.csv(enr_only,"HILO_enriched_prot.csv")
write.csv(dep_only,"HILO_depleted_prot.csv")
```

```{r enriched_depleted_tiles HIpre}
hipre_enr <- filter(hipre_tiling,LFC1>0&LFC2>0&LFC3>0&((ISREHI.rep1>100&ISREHI.rep2>100)|(ISREHI.rep1>100&ISREHI.rep3>100)|(ISREHI.rep2>100&ISREHI.rep3>100)))
hipre_dep <- filter(hipre_tiling,LFC1<0&LFC2<0&LFC3<0&((ISREHI.rep1>100&ISREHI.rep2>100)|(ISREHI.rep1>100&ISREHI.rep3>100)|(ISREHI.rep2>100&ISREHI.rep3>100)))

overlap <- filter(hipre_enr,hipre_enr$viral_protein %in% hipre_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

overlap2 <- filter(hipre_dep,hipre_dep$viral_protein %in% hipre_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

overlap <- rbind(overlap,overlap2)

enr_only <- filter(hipre_enr,!(hipre_enr$viral_protein %in% hipre_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

dep_only <- filter(hipre_dep,!(hipre_dep$viral_protein %in% hipre_enr$viral_protein)) %>%
select(viral_protein,LFC1,LFC2,LFC3, ID,protein)

hipre_overlap_venn <- distinct(overlap,viral_protein)
hipre_enr_only_venn <- distinct(enr_only,viral_protein)
hipre_dep_only_venn <- distinct(dep_only,viral_protein)

overlap
enr_only
dep_only

write.csv(overlap,"HIpre_overlapping_prot.csv")
write.csv(enr_only,"HIpre_enriched_prot.csv")
write.csv(dep_only,"HIpre_depleted_prot.csv")
```

```{r enriched_depleted_tiles LOpre}
lopre_enr <- filter(lopre_tiling,LFC1>0&LFC2>0&LFC3>0&((ISRELO.rep1>100&ISRELO.rep2>100)|(ISRELO.rep1>100&ISRELO.rep3>100)|(ISRELO.rep2>100&ISRELO.rep3>100)))
lopre_dep <- filter(lopre_tiling,LFC1<0&LFC2<0&LFC3<0&((ISRELO.rep1>100&ISRELO.rep2>100)|(ISRELO.rep1>100&ISRELO.rep3>100)|(ISRELO.rep2>100&ISRELO.rep3>100)))

overlap <- filter(lopre_enr,lopre_enr$viral_protein %in% lopre_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

overlap2 <- filter(lopre_dep,lopre_dep$viral_protein %in% lopre_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

overlap <- rbind(overlap,overlap2)

enr_only <- filter(lopre_enr,!(lopre_enr$viral_protein %in% lopre_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

dep_only <- filter(lopre_dep,!(lopre_dep$viral_protein %in% lopre_enr$viral_protein)) %>%
select(viral_protein,LFC1,LFC2,LFC3, ID,protein)

lopre_overlap_venn <- distinct(overlap,viral_protein)
lopre_enr_only_venn <- distinct(enr_only,viral_protein)
lopre_dep_only_venn <- distinct(dep_only,viral_protein)

overlap
enr_only
dep_only

write.csv(overlap,"LOpre_overlapping_prot.csv")
write.csv(enr_only,"LOpre_enriched_prot.csv")
write.csv(dep_only,"LOpre_depleted_prot.csv")
```

```{r enriched_tiles}
#determine proteins that overlap
overlap <- filter(hipre_enr,hipre_enr$viral_protein %in% lopre_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "HIpre")
overlap2 <- filter(lopre_enr,lopre_enr$viral_protein %in% hipre_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "LOpre")
overlap <- rbind(overlap,overlap2)

enr_hipre <- filter(hipre_enr,!(hipre_enr$viral_protein %in% lopre_enr$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

enr_lopre <- filter(lopre_enr,!(lopre_enr$viral_protein %in% hipre_enr$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

#now we will look at the individual tiles themselves
enr_tiles_overlap <- filter(hipre_enr,hipre_enr$ID %in% lopre_enr$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "HIpre")
enr_tiles_overlap2 <- filter(lopre_enr,lopre_enr$ID %in% hipre_enr$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "LOpre")
enr_tiles_overlap_fin <- rbind(enr_tiles_overlap,enr_tiles_overlap2)
enr_tiles_hipre <- filter(hipre_enr,!(hipre_enr$ID %in% lopre_enr$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)
enr_tiles_lopre <- filter(lopre_enr,!(lopre_enr$ID %in% hipre_enr$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)

enr_overlap_venn <- distinct(overlap,viral_protein)
enr_hipre_venn <- distinct(enr_hipre,viral_protein)
enr_lopre_venn <- distinct(enr_lopre,viral_protein)

overlap
enr_hipre
enr_lopre

write.csv(enr_tiles_overlap_fin,"HIpre_LOpre_overlapping_enriched_tiles.csv")
write.csv(enr_tiles_hipre,"enriched_tiles_HIpre_only.csv")
write.csv(enr_tiles_lopre,"enriched_tiles_LOpre_only.csv")
```

```{r depleted_tiles}
overlap <- filter(hipre_dep,hipre_dep$viral_protein %in% lopre_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "HIpre")
overlap2 <- filter(lopre_dep,lopre_dep$viral_protein %in% hipre_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "LOpre")
overlap <- rbind(overlap,overlap2)
dep_hipre <- filter(hipre_dep,!(hipre_dep$viral_protein %in% lopre_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)
dep_lopre <- filter(lopre_dep,!(lopre_dep$viral_protein %in% hipre_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3, ID,protein)

dep_tiles_overlap <- filter(hipre_dep,hipre_dep$ID %in% lopre_dep$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "HIpre")
dep_tiles_overlap2 <- filter(lopre_dep,lopre_dep$ID %in% hipre_dep$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "LOpre")
dep_tiles_overlap_fin <-rbind(dep_tiles_overlap,dep_tiles_overlap2)
dep_tiles_hipre <- filter(hipre_dep,!(hipre_dep$ID %in% lopre_dep$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)
dep_tiles_lopre <- filter(lopre_dep,!(lopre_dep$ID %in% hipre_dep$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)

dep_overlap_venn <- distinct(overlap,viral_protein)
dep_hipre_venn <- distinct(dep_hipre,viral_protein)
dep_lopre_venn <- distinct(dep_lopre,viral_protein)

overlap
dep_hipre
dep_lopre

write.csv(dep_tiles_overlap_fin,"HIpre_LOpre_overlapping_depleted_tiles.csv")
write.csv(dep_tiles_hipre,"depleted_tiles_HIpre_only.csv")
write.csv(dep_tiles_lopre,"depleted_tiles_LOpre_only.csv")
```

```{r enr_dep_tiles}
#determine proteins that overlap
overlap <- filter(hipre_enr,hipre_enr$viral_protein %in% lopre_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "HIpre")
overlap2 <- filter(lopre_dep,lopre_dep$viral_protein %in% hipre_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "LOpre")
overlap <- rbind(overlap,overlap2)

enr_dep_hipre <- filter(hipre_enr,!(hipre_enr$viral_protein %in% lopre_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

enr_dep_lopre <- filter(lopre_dep,!(lopre_dep$viral_protein %in% hipre_enr$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

#now we will look at the individual tiles themselves
enr_dep_tiles_overlap <- filter(hipre_enr,hipre_enr$ID %in% lopre_dep$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "HIpre")
enr_dep_tiles_overlap2 <- filter(lopre_dep,lopre_dep$ID %in% hipre_enr$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "LOpre")
enr_dep_tiles_overlap_fin <- rbind(enr_dep_tiles_overlap,enr_dep_tiles_overlap2)
enr_dep_tiles_hipre <- filter(hipre_enr,!(hipre_enr$ID %in% lopre_dep$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)
enr_dep_tiles_lopre <- filter(lopre_dep,!(lopre_dep$ID %in% hipre_enr$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)

enr_dep_overlap_venn <- distinct(overlap,viral_protein)
enr_dep_hipre_venn <- distinct(enr_dep_hipre,viral_protein)
enr_dep_lopre_venn <- distinct(enr_dep_lopre,viral_protein)

overlap
enr_dep_hipre
enr_dep_lopre

write.csv(enr_dep_tiles_overlap_fin,"HIpre_LOpre_overlapping_enr_dep_tiles.csv")
```

```{r dep_enr_tiles}
#determine proteins that overlap
overlap <- filter(hipre_dep,hipre_dep$viral_protein %in% lopre_enr$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "HIpre")
overlap2 <- filter(lopre_enr,lopre_enr$viral_protein %in% hipre_dep$viral_protein) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein) %>% mutate(Treat = "LOpre")
overlap <- rbind(overlap,overlap2)

dep_enr_hipre <- filter(hipre_dep,!(hipre_dep$viral_protein %in% lopre_enr$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

dep_enr_lopre <- filter(lopre_enr,!(lopre_enr$viral_protein %in% hipre_dep$viral_protein)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein)

#now we will look at the individual tiles themselves
dep_enr_tiles_overlap <- filter(hipre_dep,hipre_dep$ID %in% lopre_enr$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "HIpre")
dep_enr_tiles_overlap2 <- filter(lopre_enr,lopre_enr$ID %in% hipre_dep$ID) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq) %>% mutate(Treat = "LOpre")
dep_enr_tiles_overlap_fin <- rbind(dep_enr_tiles_overlap,dep_enr_tiles_overlap2)
dep_enr_tiles_hipre <- filter(hipre_dep,!(hipre_dep$ID %in% lopre_enr$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)
dep_enr_tiles_lopre <- filter(lopre_enr,!(lopre_enr$ID %in% hipre_dep$ID)) %>% select(viral_protein,LFC1,LFC2,LFC3,ID,protein,seq)

dep_enr_overlap_venn <- distinct(overlap,viral_protein)
dep_enr_hipre_venn <- distinct(dep_enr_hipre,viral_protein)
dep_enr_lopre_venn <- distinct(dep_enr_lopre,viral_protein)

overlap
dep_enr_hipre
dep_enr_lopre

write.csv(dep_enr_tiles_overlap_fin,"HIpre_LOpre_overlapping_dep_enr_tiles.csv")
```

## Venn diagrams

```{r venn_diagram}
library(eulerr)

hilo <- euler(c("HILO enriched" = nrow(hilo_enr_only_venn), "HILO depleted" = nrow(hilo_dep_only_venn), "HILO enriched&HILO depleted" = nrow(hilo_overlap_venn)))

hipre <- euler(c("HIpre enriched" = nrow(hipre_enr_only_venn), "HIpre depleted" = nrow(hipre_dep_only_venn), "HIpre enriched&HIpre depleted" = nrow(hipre_overlap_venn)))

lopre <- euler(c("LOpre enriched" = nrow(lopre_enr_only_venn), "LOpre depleted" = nrow(lopre_dep_only_venn), "LOpre enriched&LOpre depleted" = nrow(lopre_overlap_venn)))

enriched <- euler(c("HIpre enriched" = nrow(enr_hipre_venn), "LOpre enriched" = nrow(enr_lopre_venn), "HIpre enriched&LOpre enriched" = nrow(enr_overlap_venn)))

depleted <- euler(c("HIpre depleted" = nrow(dep_hipre_venn), "LOpre depleted" = nrow(dep_lopre_venn), "HIpre depleted&LOpre depleted" = nrow(dep_overlap_venn)))

enr_dep <- euler(c("HIpre enriched" = nrow(enr_dep_hipre_venn), "LOpre depleted" = nrow(enr_dep_lopre_venn), "HIpre enriched&LOpre depleted" = nrow(enr_dep_overlap_venn)))

dep_enr <- euler(c("HIpre depleted" = nrow(dep_enr_hipre_venn), "LOpre enriched" = nrow(dep_enr_lopre_venn), "HIpre depleted&LOpre enriched" = nrow(dep_enr_overlap_venn)))

enr_tiles <- euler(c("HIpre enr Tiles" = nrow(enr_tiles_hipre), "LOpre enr Tiles" = nrow(enr_tiles_lopre), "HIpre enr Tiles&LOpre enr Tiles" = nrow(enr_tiles_overlap)))

dep_tiles <- euler(c("HIpre dep Tiles" = nrow(dep_tiles_hipre), "LOpre dep Tiles" = nrow(dep_tiles_lopre), "HIpre dep Tiles&LOpre dep Tiles" = nrow(dep_tiles_overlap)))

enr_dep_tiles <- euler(c("HIpre enr Tiles" = nrow(enr_dep_tiles_hipre), "LOpre dep Tiles" = nrow(enr_dep_tiles_lopre), "HIpre enr Tiles&LOpre dep Tiles" = nrow(enr_dep_tiles_overlap)))

dep_enr_tiles <- euler(c("HIpre dep Tiles" = nrow(dep_enr_tiles_hipre), "LOpre enr Tiles" = nrow(dep_enr_tiles_lopre), "HIpre dep Tiles&LOpre enr Tiles" = nrow(dep_enr_tiles_overlap)))

plot(hilo,quantities =list(type=c("counts")))
plot(hipre,quantities =list(type=c("counts")))
plot(lopre,quantities =list(type=c("counts")))
plot(enriched,quantities =list(type=c("counts")))
plot(depleted,quantities =list(type=c("counts")))
plot(enr_dep,quantities =list(type=c("counts")))
plot(dep_enr,quantities =list(type=c("counts")))
plot(enr_tiles,quantities =list(type=c("counts")))
plot(dep_tiles,quantities =list(type=c("counts")))
plot(enr_dep_tiles,quantities =list(type=c("counts")))
plot(dep_enr_tiles,quantities =list(type=c("counts")))
```